Multisensor Architecture for an Intersection Management System

### 2019-01-28 ch4-results.tex
Added summary table and fixed format

Performing the same frame-based analysis as for the video system, we obtain the confusion matrices presented in table \ref{vl_cf}. It is noted that performing the fusion at virtual sensor occupancy level, the accuracy of the systems has almost no change, 92.2\% and 91.48\% for average and maximum policies respectively. For the TPR, there is a significative increase, having 88.12\% and 63.56\%, also for average and maximum policies.

@@

\begin{figure}[htb!]
\centering
\includegraphics[scale=0.4]{fig/4/conf_mat.jpeg}
\caption{Results for the multisensor implementation using four different fusion approaches}
\label{vl_res}
\end{figure}

\begin{table}[htb!]
\footnotesize
\centering
\noindent
\renewcommand\arraystretch{1.5}
\setlength\tabcolsep{0pt}
\begin{tabular}{c c c c c}
  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
     \multicolumn{4}{c}{\bfseries Outcome (avg vs\_occ)} \\
  & & \bfseries F & \bfseries S & \bfseries total \\
  & F$'$ & \MyBox{1098}{} & \MyBox{148}{} & 1246 \\[2.4em]
  & S$'$ & \MyBox{403}{} & \MyBox{5414}{} & 5817 \\
  & total & 1501 & 5562 &
\end{tabular}

\begin{tabular}{c c c c c}
  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
     \multicolumn{4}{c}{\bfseries Outcome (max vs\_occ)}  \\
  & & \bfseries F & \bfseries S & \bfseries total \\
  & F$'$ & \MyBox{792}{} & \MyBox{454}{} & 1246 \\[2.4em]
  & S$'$ & \MyBox{148}{} & \MyBox{5669}{} & 5817 \\
  & total & 940 & 6123 &
\end{tabular}

\begin{tabular}{c c c c c}
  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
     \multicolumn{4}{c}{\bfseries Outcome (avg flow)} \\
  & & \bfseries F & \bfseries S & \bfseries total \\
  & F$'$ & \MyBox{161}{} & \MyBox{1085}{} & 1246 \\[2.4em]
  & S$'$ & \MyBox{13}{} & \MyBox{5804}{} & 5817 \\
  & total & 174 & 6889 &
\end{tabular}

\begin{tabular}{c c c c c}
  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
     \multicolumn{4}{c}{\bfseries Outcome (max flow)}  \\
  & & \bfseries F & \bfseries S & \bfseries total \\
  & F$'$ & \MyBox{716}{} & \MyBox{530}{} & 1246 \\[2.4em]
  & S$'$ & \MyBox{193}{} & \MyBox{5624}{} & 5817 \\
  & total & 909 & 6154 &
\end{tabular}

\caption{Fusion configurations from top to bottom: Average on virtual sensor occupancy, Maximum on virtual sensor occupancy, Average on flow rate, Maximum on flow rate}
\label{vl_cf}
\end{table}

@@

>>>>

Performing the same frame-based analysis as for the video system, we obtain the confusion matrices presented in figure \ref{vl_cf}. It is noted that performing the fusion at virtual sensor occupancy level, the accuracy of the systems has almost no change, 92.2\% and 91.48\% for average and maximum policies respectively. For the TPR, there is a significative increase, having 88.12\% and 63.56\%, also for average and maximum policies.

@@

\begin{figure}[htb!]
\centering
\includegraphics[scale=0.4]{fig/4/conf_mat.jpeg}
\caption{Fusion configurations: top-left, Average on virtual sensor occupancy. Bottom-left, Maximum on virtual sensor occupancy. Top-right, Average on flow rate. Bottom-rigth, Maximum on flow rate}
\label{vl_cf}
\end{figure}

%\begin{table}[htb!]
%\footnotesize
%\centering
%\noindent
%\renewcommand\arraystretch{1.5}
%\setlength\tabcolsep{0pt}
%\begin{tabular}{c c c c c}
%  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
%     \multicolumn{4}{c}{\bfseries Outcome (avg vs\_occ)} \\
%  & & \bfseries F & \bfseries S & \bfseries total \\
%  & F$'$ & \MyBox{1098}{} & \MyBox{148}{} & 1246 \\[2.4em]
%  & S$'$ & \MyBox{403}{} & \MyBox{5414}{} & 5817 \\
%  & total & 1501 & 5562 &
%\end{tabular}
%
%\begin{tabular}{c c c c c}
%  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
%     \multicolumn{4}{c}{\bfseries Outcome (max vs\_occ)}  \\
%  & & \bfseries F & \bfseries S & \bfseries total \\
%  & F$'$ & \MyBox{792}{} & \MyBox{454}{} & 1246 \\[2.4em]
%  & S$'$ & \MyBox{148}{} & \MyBox{5669}{} & 5817 \\
%  & total & 940 & 6123 &
%\end{tabular}
%
%\begin{tabular}{c c c c c}
%  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
%     \multicolumn{4}{c}{\bfseries Outcome (avg flow)} \\
%  & & \bfseries F & \bfseries S & \bfseries total \\
%  & F$'$ & \MyBox{161}{} & \MyBox{1085}{} & 1246 \\[2.4em]
%  & S$'$ & \MyBox{13}{} & \MyBox{5804}{} & 5817 \\
%  & total & 174 & 6889 &
%\end{tabular}
%
%\begin{tabular}{c c c c c}
%  \multirow{10}{*}{\rotatebox{90}{\parbox{1.1cm}{\bfseries\centering Actual\\ value}}} & 
%     \multicolumn{4}{c}{\bfseries Outcome (max flow)}  \\
%  & & \bfseries F & \bfseries S & \bfseries total \\
%  & F$'$ & \MyBox{716}{} & \MyBox{530}{} & 1246 \\[2.4em]
%  & S$'$ & \MyBox{193}{} & \MyBox{5624}{} & 5817 \\
%  & total & 909 & 6154 &
%\end{tabular}
%
%\caption{Fusion configurations from top to bottom: Average on virtual sensor occupancy, Maximum on virtual sensor occupancy, Average on flow rate, Maximum on flow rate}
%\label{vl_cf}
%\end{table}

@@

\begin{table}[ht!]
\footnotesize
\begin{tabular}{c c c c c}
Test Case & Sensors & Fusion Aproaches & Accuracy & TPR \\

Case 1 & Camera & NA & 91.82\% & 55.7\% \\
Case 2 & Camera + Lasers & Low-level, Mid-level (avg) & 92.2\% & 88.12\%\\
Case 2 & Camera + Lasers & Low-level, Mid-level (max) & 91.48\% & 63.56\% \\
Case 2 & Camera + Lasers & Low-level, High-level (avg) & 84.45\% & 12.92\% \\
Case 2 & Camera + Lasers & Low-level, High-level (max) & 89.76\% & 57.46\%\\

\end{tabular}
\caption{Summary of results}
\label{results}
\end{table}
